Covariate analysis of UFL-Mayo-ISB RNASeq

### 2016-01-11 code/Rmd/Mayo_Cerebellum_RNASeq.Rmd
Minor modifications

### Data preprocessing
```{r preprocess.data,cache=TRUE, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA <- METADATA %>%
  dplyr::filter(!(SampleID %in% c("742_CER")))
```

```{r preprocess.data1,cache=TRUE}
indToRetain = intersect(METADATA$SampleID, colnames(COUNT))

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(Diagnosis), shape=as.factor(Source), size=as.numeric(AgeAtDeath)))
p <- p + theme_bw() + theme(legend.position="top") 
# p <- p + geom_text(aes(label= SampleID), size=4, hjust=0)
p
```
### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, results='asis', echo=FALSE}
# Find correlation between PC's of gene expression with covariates
DESIGN = getDesignMat2Fact(DM$design,FactorCovariates)
colnames(DESIGN) = substr(colnames(DESIGN),1,50)
preAdjustedSigCovars = runPCAandPlotCorrelations(VOOM.GENE_EXPRESSION$E, DESIGN,
                                                 'NULL design(voom-normalized)',
                                                 isKeyPlot=TRUE)

>>>>

### Data preprocessing
```{r preprocess.data,cache=TRUE, echo=TRUE}
# Fix metadata
METADATA$AgeAtDeath = gsub("_or_above", "", METADATA$AgeAtDeath)
METADATA <- METADATA %>%
  dplyr::filter(!(SampleID %in% c("742_CER", "11386_CER","11311_CER","1923_CER","1147_CER")))
```
Following five samples were considered outliers and removed 742_CER, 11386_CER, 11311_CER, 1923_CER, 1147_CER
```{r preprocess.data1,cache=TRUE}
indToRetain = intersect(METADATA$SampleID, colnames(COUNT))

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=factor(Diagnosis), shape=as.factor(Source), size=as.numeric(AgeAtDeath)))
p <- p + theme_bw() + theme(legend.position="top") 
p <- p + geom_text(aes(label= SampleID), size=4, hjust=0)
p

# Tree based clustering
sampleTrees = flashClust::hclust(dist(t(VOOM.GENE_EXPRESSION$E)), method = "average")
tree = WGCNA::cutreeStatic(sampleTrees, cutHeight = 200, minSize=3)

WGCNA::plotDendroAndColors(sampleTrees, 
                    labels2colors(cbind(tree,COVARIATES)),
                    groupLabels = c('Cluster',colnames(COVARIATES)))
collectGarbage()
```

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, results='asis', echo=FALSE}
# Find correlation between PC's of gene expression with covariates
DESIGN = getDesignMat2Fact(DM$design,FactorCovariates)
colnames(DESIGN) = substr(colnames(DESIGN),1,50)
preAdjustedSigCovars = runPCAandPlotCorrelations(VOOM.GENE_EXPRESSION$E, DESIGN,
                                                 'NULL design(voom-normalized)',
                                                 isKeyPlot=TRUE)
